\documentclass[../DoAn.tex]{subfiles}
\begin{document}

\begin{center}
    \Large{\textbf{ABSTRACT}}\\
\end{center}
\vspace{1cm}
In the context of increasingly complex cybersecurity risks, protecting internal communication systems has become a top priority, driving the adoption of end-to-end encryption (E2EE) as an essential security solution. Currently, most leading E2EE messaging applications operate based on the Double Ratchet protocol, a standard that exhibits many limitations when scaling to group communications. To address this issue, Messaging Layer Security (MLS) emerged as a pioneering protocol, comprehensively redefining the group encryption architecture. However, the current MLS specification has a major academic gap: it is designed exclusively for centralized architectures and is forced to rely on a delivery service server to ensure ordering. Implementing MLS in decentralized peer-to-peer (P2P) network environments remains an unsolved challenge. From this practical reality, I decided to pursue a research direction that directly integrates the MLS protocol onto P2P network architectures, completely removing the central server. This direction was chosen to demonstrate the fusion between the most advanced group encryption standard today and the philosophy of decentralized networks, thereby outlining a theoretical model for a communication system without a single point of failure. The overview of the proposed solution is to introduce a decentralized delivery service layer. This architecture completely replaces the role of the server in managing group state updates, while providing the ability to automatically maintain consensus, detect, and heal branches when phân vùng mạnging occurs. The core contribution of this thesis is the successful establishment of a complete solution for the MLS application model in P2P networks, culminating in a stably operating prototype application that directly validates the research's correctness and opens a solid reference foundation for future security systems.
\end{document}